### 2021-07-08 rad-icfp-2021/relwork.tex
minor

\noindent \textbf{Higher-order functions}
TODO
Matthijs'work, use of defunctionalization, question efficiency and usefulness, 
interested in functions like root of function or minimal of a function. Implicit function theorem
Some recent work \cite{vakar2020reverse,sherman2021} present reverse-mode in a higher-order language.
\cite{vakar2020reverse} uses categorical semantics to show correctness of the reverse-mode transformation 
and \cite{sherman2021} uses sophisticated higher-order primitives such as root finding, max, argmax or integral. 
Their work focuses on computable reals which is hard to compare in terms of efficiency 
with our more standard approach of AD.

\noindent \textbf{More array primitives}
We focused on giving reverse derivatives for a small set of array primitives. 
Other common primitives include filter, flatten, gather. 
These functions can easily be added to our Source language once we provide a reverse derivative for them.
This is reminiscent of hand-crafted derivatives present in large AD frameworks (usually hundreds), 
and these can already be added in added in our language. 
One only needs to make sure that the provided transpose Jacobian is correct.

@@

TODO: understand related work sentence from Diff. Curry paper: The idea of using closures as back-propagators is receiving recent attention. 
    For example Julia Zygote \cite{innes2019zygote} and Swift AD \cite{wei2018first} chose this design. 
    Other recent work follows similar ideas [27, 26] but is using meta-programming as an implementation technique.

TODO: should talk a bit about the recent paper: reverse AD in Dex \cite{paszke2021getting}

@@

TODO
\cite{lee2020correctness}: non diff function
\cite{sherman2021}: non diff HO functions
\cite{pearlmutter2008reverse}: based on this
\cite{elliott2018simple}: bit similar because using CT as useful language, but we take impl and opti more seriously.
\cite{shaikhha2019efficient}: similar approach but here more complicated for reverse mode, would be interesting to investigate more loop fusions here.

>>>>

\noindent \textbf{Higher-order functions}
Some recent work \cite{vakar2020reverse,sherman2021} present reverse-mode in a higher-order language.
\cite{vakar2020reverse} uses categorical semantics to show correctness of the reverse-mode transformation 
and \cite{sherman2021} uses sophisticated higher-order primitives such as root finding, max, argmax or integral. 
Their work focuses on computable reals which is hard to compare in terms of efficiency with our more standard approach of AD.
It is however quite difficult to prove a complexity result in the higher-order setting. 
In addition, standard techniques of defunctionalization struggle when higher-order is combined with recursion.

\noindent \textbf{Array primitives}
We focused on giving reverse derivatives for a small set of array primitives. 
Other common primitives include filter, flatten, gather. 
These functions can easily be added to our Source language once we provide a reverse derivative for them.
This is reminiscent of hand-crafted derivatives present in large AD frameworks (usually hundreds), 
and these can already be added in added in our language. 
As shown in \ref{sub:lift_recipe}, one mostly only needs to make sure that the provided transpose Jacobian is correct.

@@

@@

TODO
\cite{lee2020correctness}: non diff function
\cite{sherman2021}: non diff HO functions
\cite{pearlmutter2008reverse}: based on this
\cite{elliott2018simple}: bit similar because using CT as useful language, but we take impl and opti more seriously.
\cite{shaikhha2019efficient}: similar approach but here more complicated for reverse mode, would be interesting to investigate more loop fusions here.
\cite{paszke2021getting}
Curry paper: The idea of using closures as back-propagators is receiving recent attention. 
    For example Julia Zygote \cite{innes2019zygote} and Swift AD \cite{wei2018first} chose this design. 
    Other recent work follows similar ideas [27, 26] but is using meta-programming as an implementation technique.
